\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx} % Police Times New Roman
% Marges optimisées pour tenir sur une page
\usepackage[left=0.45in,top=0.3in,right=0.45in,bottom=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}

% --- COULEURS ET LIENS ---
\definecolor{linkblue}{RGB}{0,0,255}
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    pdfborderstyle={/S/U/W 1}
}

% --- FORMATAGE DES TITRES ---
\titleformat{\section}
  {\normalfont\large\bfseries\uppercase}
  {}
  {0em}
  {}
  [\titlerule]

\titlespacing{\section}{0pt}{6pt}{3pt}

% --- PARAMETRES COLONNES ---
\newlength{\datecolwidth}
\setlength{\datecolwidth}{2.4cm}

% --- CONFIGURATION DES LISTES ---
\setlist[itemize]{
    label=-, 
    leftmargin=*, 
    nosep, 
    before=\vspace{-0.5\baselineskip}, 
    after=\vspace{0pt}
}

% --- MACRO CV OPTIMISÉE POUR L'ALIGNEMENT ---
% #1=Date, #2=Entité, #3=Lieu, #4=Titre/Diplôme, #5=Description
% Changement clé : Entité et Titre sont dans la MEME cellule séparés par \newline
% Cela garantit que la ligne 2 de la date s'aligne avec la ligne 2 du texte (Titre)
\newcommand{\CVItem}[5]{%
    \noindent%
    \begin{tabularx}{\textwidth}{@{}p{\datecolwidth} X@{}}
        #1 & \textbf{#2} \hfill #3 \newline \textit{#4} \\ % Entité et Titre fusionnés
           & #5 
    \end{tabularx}%
    \vspace{2pt}%
}

\pagestyle{empty}

\begin{document}

% --- EN-TÊTE CORRIGÉ (ALIGNEMENT PARFAIT) ---
% Utilisation d'un tabular pour forcer le centrage relatif strict
\begin{center}
    \begin{tabular}{c}
        {\huge \textbf{Nicolas Grimaldi}} \\[3pt]
        \href{mailto:Nicolas.grimaldi@hec.edu}{Nicolas.grimaldi@hec.edu} \ $|$ \ +33 6 48 32 96 74 \ $|$ \ \href{https://www.linkedin.com/in/nicolas-grimaldi-a893b6246/}{Linkedin}
    \end{tabular}
\end{center}

\vspace{-8pt}

% --- EDUCATION ---
\section{Education}

\CVItem{2025 -- 2027}
    {ENSAE, Institut Polytechnique de Paris}
    {Paris, France}
    {Master in Science | Double Degree with HEC Paris}
    {Top-tier French Grande École specializing in statistics, data science, economics, and quantitative finance \newline
     Relevant courses: Time Series Analysis, Stochastic Process, Statistics, Machine Learning}

\CVItem{2023 -- 2027}
    {HEC Paris}
    {Paris, France}
    {Master in Management}
    {Ranked \#1 Master in Management by QS \newline
     Relevant courses: Financial Economics, Markets Finance, Data Modelling, Accounting, Data Science \newline
     GPA: 3.9 / 4.0}

\CVItem{2023 -- 2024}
    {Université Paris-Saclay}
    {Versailles, France}
    {Bachelor’s degree in Mathematics | In parallel with First Year at HEC}
    {Ranked \#2 University for Mathematics in the world by Shanghai Ranking \newline
     Relevant courses: Advanced Probability, Optimization, Python \newline
     GPA: 4/4}

\CVItem{2021 -- 2023}
    {Lycée Notre-Dame du Grandchamp}
    {Versailles, France}
    {Classes préparatoires, Intensive program for entrance to top French Business schools}
    {Majors: Advanced Mathematics (Algebra, Analysis, Probability) and Geopolitics}

% --- PROFESSIONAL EXPERIENCE ---
\section{Professional Experience}

% Utilisation de \newline dans la date pour aligner l'année avec le poste
\CVItem{Oct -- Present \newline 2025 -- 2026}
    {Red River West}
    {Paris, France}
    {Data Science assistant}
    {\begin{itemize}
        \item Developing and validating predictive startup survival models.
    \end{itemize}}

\CVItem{March -- Sept \newline 2025}
    {QuantCube Technology}
    {Paris, France}
    {Data Research Intern}
    {\begin{itemize}
        \item Led an end-to-end research project designing a completeness score to measure coverage and reliability of corporate asset data.
        \item Collected, cleaned, and structured datasets by linking financial indicators and validated assets, enabling quantitative analysis.
        \item Implemented predictive models (Random Forests, Gradient Boosting) to estimate missing asset data.
        \item Benchmarked models and delivered sector-level insights to guide database enrichment strategies.
    \end{itemize}}

\CVItem{2023 -- 2025}
    {Private Mathematics Teacher}
    {Paris, France}
    {Tutor}
    {\begin{itemize}
        \item Provided personalised tutoring to students in preparatory classes for French business schools (ECG), with a focus on advanced mathematics to prepare for competitive entrance exams.
        \item 3 out of the 4 students I coached reached the top 3 of their class in math.
    \end{itemize}}

% --- EXTRACURRICULAR ACTIVITIES ---
\section{Extracurricular Activities}

\CVItem{2025 -- Present}
    {\href{https://goodtoshare.io}{GoodToShare.io}}
    {Paris, France}
    {Co-founder}
    {\begin{itemize}
        \item Developed a marketplace enabling users to monetize networks via qualified business introductions.
        \item Designed platform connecting high-quality solutions with decision-makers via trusted community referrals.
    \end{itemize}}

\CVItem{Sept -- June \newline 2023 -- 2025}
    {HEC DataMinds}
    {Jouy-en-Josas, France}
    {Member / Analyst}
    {\begin{itemize}
        \item Developed Python/VBA demand-forecasting models, improving inventory accuracy by 15\%.
    \end{itemize}}

% --- SKILLS & INTERESTS ---
\section{Skills \& Interests}

\noindent
\begin{tabularx}{\textwidth}{@{}p{\datecolwidth} X@{}}
    \textbf{Languages} & French (native), English (fluent, TOEFL IBT: 115/120), Spanish (B2 intermediate) \\
    \textbf{IT Skills} & Python, SQL, VBA, C++, Bloomberg Terminal \\
    \textbf{Certifications} & Hi Paris! Data Bootcamp (with Ecole Polytechnique), Machine Learning for Finance in Python (Datacamp), Machine Learning and Deep Learning (Coursera). \\
    \textbf{Interests} & Soccer (Vice-captain, HEC men’s team), Chess (1900 elo on chess.com)
\end{tabularx}

\end{document}